---
title: "DaEx!"
author: "Luca Cerone"
date: "May 6, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
suppressMessages({
  knitr::opts_chunk$set(echo = FALSE)
  library(plotly)
  library(dplyr)
})
```

## Datasets Explorer!

With "DaEx!" (**Datasets Explorer!**) you can:

- Select a dataset of you choice
- Plot any two numeric variables in the dataset using a scatterplot
- Select which variable should be on the x-axis and which variable should by on the y-axes

## Automatic detection of numeric variables

DaEx! figures out which variables are suitable to be visualized by a scatterplot!

- Only the numeric variables can be used in the plot

## Automatic detection of numeric variables 

This is what happens under the hood when you select iris

```{r, echo = TRUE}
    dataset <- iris
    cols <- colnames(dataset)
    is_numeric <- sapply(dataset,is.numeric)
    cols[is_numeric]
```

Species is discarded because it is a factor

## Scatterplot in the main panel

Here is an example of a scatterplot shown by DaEx!

```{r, echo = TRUE, tidy=F}
dataset <- iris %>% select(x = Sepal.Length, y = Petal.Width)
p <- plot_ly(dataset, x = ~x, y = ~y, 
             type = "scatter", mode = "markers")
p
```

